Article title

### 2017-07-28 paper-webserver.tex
CHANGE: slight rewrite of potentials para

% potential of WGS
WGS expands on traditional methods: due to the inclusion of the entire genome, WGS-based methods offer better resolution and context for evaluating the spread of outbreaks \cite{ronholm2016navigating}.
In the case of laboratory-based MLST, instead of examining selected single-nucleotide polymorphisms (SNPs) in a subset of housekeeping genes, newer WGS-based methods, such as core genome MLST (cgMLST), attempt to cover every common gene.
Secondary analyses, the study of relations and historical relevance of genomes, are possible as a result of the large datasets provided by WGS \cite{ronholm2016navigating}.
Advances in WGS technologies have also enabled the real-time monitoring and sharing of outbreak genomes \cite{ronholm2016navigating}.

% Drawbacks - genetics
However, these WGS-based methods still examine the underlying genetics, not the expressed phenotype; the presence of a particular gene sequence does not necessitate expression.
Correspondingly, a greater number of target sequences are identified using WGS approaches which complicates risk assessments \cite{ronholm2016navigating}, and laboratory based phenotypic tests remain inexpensive \cite{koser2012routine}.
The effectiveness of WGS-based methods also rely on the accuracy and breadth of reference datasets.

>>>>

% potential of WGS
WGS expands on traditional methods: due to the inclusion of the entire genome, WGS-based methods offer better resolution and context for evaluating the spread of outbreaks \cite{ronholm2016navigating}.
In the case of laboratory-based MLST, instead of examining selected single-nucleotide polymorphisms (SNPs) in a subset of housekeeping genes, newer WGS-based methods, such as core genome MLST (cgMLST), attempt to cover every common gene.
We can also detect the presence of every known virulence factor (VF) or antimicrobial resistance (AMR) gene in a WGS result.
Furthermore, using WGS we can study the relations between genomes, changes in the VF or AMR genes present over time, and mutations in gene \cite{ronholm2016navigating}.
Entire datasets and results can also be shared in real-time \cite{ronholm2016navigating}.

% Drawbacks - genetics
However, these WGS-based methods only examine the underlying genetics, not the expressed phenotype; the presence of a particular gene sequence does not necessitate expression.
Correspondingly, a greater number of target sequences are identified using WGS approaches which complicates risk assessments \cite{ronholm2016navigating}, and laboratory based phenotypic tests remain inexpensive \cite{koser2012routine}.
The effectiveness of WGS-based methods also rely on the accuracy and breadth of reference datasets.
